Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-05-09 doc/PRF2022/PRF_main.tex
update

@@

Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow
\begin{equation}
\uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx)\sin({\bf e}_y\cdot\xx){\bf e}_x+\sin({\bf e}_x\cdot\xx)\cos({\bf e}_y\cdot\xx){\bf e}_y\right).
\end{equation}
%
The magnitude of the vortex flow is controlled by the velocity scale $V_0$.

@@

>>>>

We measure the end-to-end distance of the multi-lamellar structure when the flow is on.

@@

Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow with a length scale $l$
\begin{equation}
\uu_\infty(\xx) = V_0 \left(-\cos(l{\bf e}_x\cdot\xx)\sin(l{\bf e}_y\cdot\xx){\bf e}_x+\sin(l{\bf e}_x\cdot\xx)\cos(l{\bf e}_y\cdot\xx){\bf e}_y\right).
\end{equation}
%
The magnitude of the vortex flow is controlled by the velocity scale $V_0$.

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{VesConf_0.png}
  \includegraphics[width=0.4\textwidth]{VesConf_2000.png}\\
  \includegraphics[width=0.4\textwidth]{VesConf_5000.png}
  \includegraphics[width=0.4\textwidth]{VesConf_10000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:confined_vesicle} A JP vesicle confined in a narrow channel where $N_b=25$ and $\dot\gamma=0.01$.  }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{MultConf_100.png}
  \includegraphics[width=0.4\textwidth]{MultConf_600.png}\\
  \includegraphics[width=0.4\textwidth]{MultConf_1200.png}
  \includegraphics[width=0.4\textwidth]{MultConf_2400.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:confined_lamellar} A JP multi-lamellar structure confined in a narrow channel where $N_b=40$ and $\dot\gamma=0.05$.  }
\end{figure}
